---
title: "Ch. 3:Data Visualization"
output: github_document
---

##3.1 Prerequisites
```{r}
library(tidyverse)
library(ggplot2)
#> ── Attaching packages ────────────────────────────────── tidyverse 1.2.1 ──
#> ✔ ggplot2 3.1.0.9000     ✔ purrr   0.2.5     
#> ✔ tibble  2.0.0          ✔ dplyr   0.7.8     
#> ✔ tidyr   0.8.2          ✔ stringr 1.3.1     
#> ✔ readr   1.3.1          ✔ forcats 0.3.0
#> ── Conflicts ───────────────────────────────────── tidyverse_conflicts() ──
#> ✖ dplyr::filter() masks stats::filter()
#> ✖ dplyr::lag()    masks stats::lag()
```

##3.2 

####Question:
Do cars with big engines use more fuel than cars with small engines? You probably already have an answer, but try to make your answer precise. What does the relationship between engine size and fuel efficiency look like? Is it positive? Negative? Linear? Nonlinear?

```{r}
mpg
```

Among the variables in mpg are:
1. displ, a car’s engine size, in litres.
2. hwy, a car’s fuel efficiency on the highway, in miles per gallon (mpg). A car with a low fuel efficiency consumes more fuel than a car with a high fuel efficiency when they travel the same distance.

###Plotting mpg
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))
```

###Graphing Template
ggplot(data = <DATA>) + 
  <GEOM_FUNCTION>(mapping = aes(<MAPPINGS>))

###3.2.4 Excersizes
1. Run ggplot(data = mpg). Nothing shows up on this graph when I run it just like this
```{r}
ggplot(data = mpg)
```
2. How many rows are in mpg? How many columns?
3. What does the drv variable describe? Read the help for ?mpg to find out.
4. Make a scatterplot of hwy vs cyl.
5. What happens if you make a scatterplot of class vs drv? Why is the plot not useful?

##3.3 Asthetic Mappings

Mapping the colors of the points to the class
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = class))
```

Mapping size to class (ou get an error because this is not a good idea to use size)
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, size = class))
```

Mapping class to the alpha aesthetic
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, alpha = class))
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, shape = class))
```

Making the points blue
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), color = "blue")
```

You’ll need to pick a level that makes sense for that aesthetic:
>The name of a color as a character string.  
>The size of a point in mm.  
>The shape of a point as a number, as shown in Figure 3.1.

####3.3.1 Excersizes
1. What’s gone wrong with this code? Why are the points not blue?
>ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))

The color argument should be listed outside of the parenthesis.

2. Which variables in mpg are categorical? Which variables are continuous? 
Model, trans, fl, drv, and class are all qualitative variables. Displ, year, cyl, and cty are qualitative.

3. Map a continuous variable to color, size, and shape. How do these aesthetics behave differently for categorical vs. continuous variables?
```{r}

```

4. What happens if you map the same variable to multiple aesthetics?

5. What does the stroke aesthetic do? What shapes does it work with? (Hint: use ?geom_point)

6. What happens if you map an aesthetic to something other than a variable name, like aes(colour = displ < 5)? Note, you’ll also need to specify x and y.

##3.4 Common Problems











